### 2014-02-28 paper/real.tex

\section{Real world languages}
\label{sec:real}
\cut{

>>>>

\section{Real world languages}
\label{sec:real}

In this section we consider the application of our embedding to 
real world target languages.
%
To illustrate the flexibility of our system and challenges in the
embedding we chose three mainstream languages---C, Haskell, and
JavaScript---that have vastly different features and properties.
%
We remark that we have implemented variants of our Haskell and
JavaScript embeddings, which are used in the Hails~\tocite{} and
SWAPI~\tocite{} systems; we leave the implementation of the IFC system
for C, as describe below, to future work.

\subsection{C}
\label{sec:real:c}

\subsection{Haskell}
\label{sec:real:hs}
While the C embedding closely resembles the specification language of
Section~\ref{sec:retrofit}, in our Haskell IFC embedding we leverage
Haskell's strong data abstraction and static type system, monadic
approach to effects, and lightweight concurrency to implement the
embedding in a more efficient manner, as library.

To this end, we define a new monad, |LIO|, that wraps Haskell's |IO|
monad---which allows for arbitrary effects---to associate labels with
threads (tasks) and restrict computational effects according to the
semantics of Section~\ref{sec:retrofit}.
%
The precise restrictions encode our IFC system as computations in the
|LIO| monad.
%
By wrapping |IO|, we can use Haskell's efficient implementation of
threads, channels, etc. (e.g., we use Haskell's \texttt{forkIO} to
fork a lightweight thread in the case of |fork|), in contrast to
defining them in a pure fashion (see Section~\ref{sec:monad}).

Importantly, this concrete implementation approach also directly
corresponds to the specification language.
%
Specifically, it is |specLang alpha targetLangHS|, for $|alpha| \in
|{roundrobinf, seqf}|$, with the pure subset of Haskell as to target
language |targetLangHS|, the subset of Haskell that additionally
contains the |LIO| monad (and corresponding |LIO| computations
encoding the language) as the IFC language.
%
Of course since our IFC system is implemented as a library in Haskell,
we must ensure that these languages are indeed the subsets of Haskell
we claim, i.e., while the concrete language is all of Haskell, we must
ensure that we can restrict programs to our subset of Haskell that
encodes the combined language.
%

To this end, we rely Haskell's strong data abstraction and type system
(as enforced by Safe Haskell~\cite{Terei:2012:SH:2364506.2364524}) to
ensure that arbitrary |IO| actions cannot be lifted into
|LIO|.\footnote{
Of course, our IFC guarantees only extend insofar as the program is
written as a computation in the |LIO| monad; a program written
directly in the |IO| monad can trivially violate information flow
control.
}
%
In other words, assuming |LIO| is implemented correctly, programs
written in the |LIO| monad cannot perform arbitrary |IO| actions
without breaking abstraction.

We refer the interested reader to~\tocite{icfp,haskellsymp} for
additional details on the various implementations of this system.
%
Finally, we remark that in this work unifies these systems and
presents in addition to proving NI fo such systems with asynchronous
communication primitives.

\subsection{JavaScript}
\label{sec:real:js}

\cut{
